GRASS: Distinguishing Planet-induced Doppler Signatures from Granulation with a Synthetic Spectra Generator

### 2022-08-30 src/tex/ms.tex
[showyourwork] overleaf sync

% \input{captions/fig2.tex}
\begin{figure*}
    \epsscale{1.1}
    \plottwo{fig2a.pdf}{fig2b.pdf}
    \caption{Example pre-processed input data showing granular variability at disk center ($\mu = 1$). Each curve shows the input data at one snapshot in time. The color gradient has been added to aid the eye in separating out these realizations. \textbf{Left:} Line bisectors show variation due to pulsations and granulation. Changes in bisector shape encode granulation, and changes in position result from the combined effects of pulsations and granulation. Above continuum-normalized flux of 0.8 \revise{(gray hatched region)}, we model the bisector as the extrapolation from lower flux values. \textbf{Right:} Line widths measured as a function of depth show \revise{only slight} variation with time. These width measurements display significantly less \revise{temporal} variability compared to the line bisectors. Together, line bisectors and width as a function of depth uniquely specify the shape of a line at a given instance in time.}
    \label{fig:two}
    \script{fig2.jl}
\end{figure*}{}

@@

% \input{captions/fig3.tex}

>>>>

% \input{captions/fig2.tex}
\begin{figure*}
    \epsscale{1.1}
    \plottwo{figures/fig2a.pdf}{figures/fig2b.pdf}
    \caption{Example pre-processed input data showing granular variability at disk center ($\mu = 1$). Each curve shows the input data at one snapshot in time. The color gradient has been added to aid the eye in separating out these realizations. \textbf{Left:} Line bisectors show variation due to pulsations and granulation. Changes in bisector shape encode granulation, and changes in position result from the combined effects of pulsations and granulation. Above continuum-normalized flux of 0.8 \revise{(gray hatched region)}, we model the bisector as the extrapolation from lower flux values. \textbf{Right:} Line widths measured as a function of depth show \revise{only slight} variation with time. These width measurements display significantly less \revise{temporal} variability compared to the line bisectors. Together, line bisectors and width as a function of depth uniquely specify the shape of a line at a given instance in time.}
    \label{fig:two}
    \script{fig2.jl}
\end{figure*}{}

@@

% \input{captions/fig3.tex}
\begin{figure*}
    \epsscale{1.15}
    \plottwo{figures/fig3a.pdf}{figures/fig3b.pdf}
    \caption{Validation of \grass\ line synthesis against the IAG solar atlas. \textbf{Left:} Observed (blue) and synthetic (black) Fe I 5434.5 \AA\ absorption lines in disk integrated light are overplotted. We additionally plot the IAG spectrum cleaned of shallow line blends in green, which nearly completely covers the black synthetic curve. Residuals between the IAG spectrum and the synthetic spectrum are shown in the bottom panel. Our synthetic spectrum deviates from the observed IAG spectrum at most by $\sim$5\% (blue squares), but only by $\sim$0.5\% from the cleaned IAG spectrum (green circles). \textbf{Right:} The observed IAG (blue) and synthetic (black) Fe I 5434.5 \AA\ bisectors, which have been arbitrarily shifted horizontally (i.e., in velocity) to achieve maximal alignment, generally agree in shape up to 60\% of the continuum level. The cleaned IAG (green) and synthetic bisectors are in much greater agreement. The residuals shown in the right panel further show that the blend cleaning greatly improves the agreement between model and observation, especially in the upper portion of the bisector.}
    \label{fig:compare_solar}
    \script{fig3.jl}
\end{figure*}{}
